
\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{geometry}
\geometry{left=1cm,right=1cm,top=1cm,bottom=1cm}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\newcommand{\resumeItem}[1]{\item{\small{#1}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item[]
    {\textbf{#1}} \hfill {#2}\\
    {\textit{#3}} \hfill {#4}\\
}
\newcommand{\resumeSubItem}[2]{\item[] \textbf{#1}: #2}
\newcommand{\resumeSubSubheading}[2]{\item[]\textbf{#1}\hfill{#2}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Khushal Mishra}} \\ 
  Dehradun, India $\cdot$ 7976457673 $\cdot$ \href{mailto:1000018098@dit.edu.in}{1000018098@dit.edu.in} \\ 
  \href{https://linkedin.com/in/khushalmishra11}{linkedin.com/in/khushalmishra11} $\cdot$ 
  \href{https://github.com/khushalmishra11}{github.com/khushalmishra11} $\cdot$ 
  \href{https://khushalmishra.vercel.app}{khushalmishra.vercel.app} \\ 
\end{center}

\section*{Summary}
Final-year B.Tech Computer Science student with strong foundation in web development and automation. Experienced in Puppeteer, React, and building scalable personal projects.

\section*{Education}
\begin{itemize}[leftmargin=*]
  \resumeSubheading{DIT University}{2025}{Bachelor in Technology in Computer Science and Engineering}{CGPA: 8.01}
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} Java, C, C++
  \item \textbf{Frontend:} HTML, CSS (TailwindCSS), JavaScript, ReactJs
  \item \textbf{Backend:} Node.js, MongoDB, SQL
  \item \textbf{Tools/Other:} Git, GitHub, VSCode, CursorAI, IntelliJ
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
  \item \textbf{Internshala Automation Bot (Apr 2025 -- Jun 2025):}
  \begin{itemize}
    \item Developed an automated solution to apply for internships on Internshala using Puppeteer, Node.js, and JavaScript.
    \item Designed to parse and auto-fill resume-based data, allowing bulk applications to up to 10 listings.
    \item Reduced manual effort significantly, improving application efficiency and speed.
  \end{itemize}
\end{itemize}

\section*{Practice Projects}
\begin{itemize}[leftmargin=*]
  \item \textbf{Uber Clone:} Recreated Uber's core UI and logic as a practice project.
  \item \textbf{JSAP Animated Website (Static):} Developed a fully animated static webpage with JavaScript and HTML/CSS.
  \item \textbf{Uifry Webpage:} UI/UX clone of Uifry to showcase frontend design skills.
\end{itemize}

\section*{Achievements}
\begin{itemize}[leftmargin=*]
  \item Solved 500+ Problems on LeetCode: \href{https://www.leetcode.com/u/khushalmishra11}{leetcode.com/u/khushalmishra11}
  \item GeeksforGeeks University Rank 463: \href{https://www.geeksforgeeks.org/user/khushalmishra11/}{geeksforgeeks.org/user/khushalmishra11/}
\end{itemize}

\end{document}
